RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
typo fix

Though certain functions allow R users to switch between these formats
within R, these formats frequently contain more information than their
NEXUS file counterparts, and users lack a suitable alternative for
archiving and sharing phylogenetic data outside of the R ecosystem. 
Consequently, information added to phylogenies by these R programs cannot 
easily be shared, archived, and made available to other software;
but inherits the limiations of the NEXUS format.

>>>>

Though certain functions allow R users to switch between these formats
within R, these formats frequently contain more information than their
NEXUS file counterparts, and users lack a suitable alternative for
archiving and sharing phylogenetic data outside of the R ecosystem. 
Consequently, information added to phylogenies by these R programs cannot 
easily be shared, archived, and made available to other software;
but inherits the limitations of the NEXUS format.
